---
title: "UCT_estimate_code_share"
author: "Nick_Fox"
date: "7/13/2018"
output: html_document
---

The following is code used to generate the unmatched count estimate (UCT) and bootstrapped 95% confidence intervals of the proportion of American psychologists who have used at least one Questionable Research Practice in the past 12 months -  from Fox, Honeycutt, and Jussim 2018.  Please direct any questions to Nick Fox at nwf7@psych.rutgers.edu.

To see the output generated from the data, simply hit the knit button!

---------

From the 'boot' package, the estimate is output as "t1*".  For more info about the 'boot' package, see its documentation on CRAN: https://cran.r-project.org/web/packages/boot/boot.pdf

```{r echo = FALSE}
#install packages - remove the hashtag if you need to install these packages, otherwise keep them hashed out.
#install.packages("tidyverse")
#install.packages("boot")

#load packages
suppressWarnings(suppressPackageStartupMessages(library(tidyverse)))
suppressWarnings(suppressPackageStartupMessages(library(boot)))

```

```{r echo = FALSE}

#reading in the data
#you'll want to have the data file 'direct_estimate_share' in your working directory.

UCT_data <- read.csv(".csv", header = TRUE)

```